---
title: "Code Demo"
author: "Sabir Meah"
date: "2023-05-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(survival)
library(MatchIt)
```

# Data Generation

We generate a sample of 1,000 tests to use for the generation. Variables include an indicator for booster status, an indicator for test result, and three covariates: one continuous, one categorical, and one binary.

```{r}
set.seed(612421)

data <- cbind.data.frame(
  Booster = as.factor(sample(c(0, 1), size = 1000, prob = c(0.5, 0.5), replace = TRUE)), # Indicator for if individual received booster or not (0 no, 1 yes)
  Test_Result = as.factor(sample(c(0, 1), size = 1000, prob = c(0.8, 0.2), replace = TRUE)), # Indicator for PCR test result (0 negative, 1 positive)
  Covariate_Continuous = runif(n = 1000, min = 0, max = 50), # Continuous covariate ranging between 0 and 50
  Covariate_Categorical = as.factor(sample(c("A", "B", "C", "D", "E"), size = 1000, prob = rep(0.2, 5), replace = TRUE)), # Categorical covariate with 5 levels
  Covariate_Binary = as.factor(sample(c(0, 1), size = 1000, prob = c(0.5, 0.5), replace = TRUE)) # Binary covariate
)
```

# Models Without Matching or Propensity Scores

## Models

### Unadjusted Model

```{r}
mod_unadj <- glm(Test_Result ~ Booster, family = "binomial", data = data)
summary(mod_unadj)
paste("VE =", 1 - exp(coef(mod_unadj)["Booster1"]))
```

### Adjusted Model

```{r}
mod_adj <- glm(Test_Result ~ Booster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, family = "binomial", data = data)
summary(mod_adj)
paste("VE =", 1 - exp(coef(mod_adj)["Booster1"]))
```

# Exact Matching

## Match Generation

This dataframe will be used for the propensity score adjustment and IPW models.

```{r}
# Binning continuous covariate
# Can be done along any division of your choosing, specify cutpoints with 'breaks' argument
data <- data %>%
  mutate(Covariate_Continuous_Binned = cut(Covariate_Continuous, breaks = seq(0, 50, by = 10)))
```

This dataframe will be used for just the propensity score caliper matching model.

```{r}
# Generate exact matches
# Make sure to use the binned version of the continuous covariate
data_exact_match <- matchit(Booster ~ Covariate_Continuous_Binned + Covariate_Categorical + Covariate_Binary, 
                             data = data, 
                             method = "exact") %>%
  match.data() # This function call is necessary for a dataframe to be output
# Matching strata of observations are denoted by new 'subclass' column in dataframe
```

## Matched Models

### Unconditional Logisitic Regression

```{r}
mod_exact_lr <- glm(Test_Result ~ Booster, family = "binomial", data = data_exact_match)
summary(mod_exact_lr)
paste("VE =", 1 - exp(coef(mod_exact_lr)["Booster1"]))
```

### Conditional Logistic Regression

```{r}
# 'clogit()' requires a numeric or logical outcome variable
# Given that we stored 'Test_Result' as a factor, we coerce it to a numeric variable
mod_exact_clr <- clogit(as.numeric(Test_Result) ~ Booster + strata(subclass), data = data_exact_match)
summary(mod_exact_clr)
paste("VE =", 1 - exp(coef(mod_exact_clr)["Booster1"]))
```

# Propensity Score Models

## Propensity Score Generation

```{r}
# Logisitic model generating propensity score by predicting exposure (vaccination)
propensity_boosting_mod <- glm(Booster ~ Covariate_Continuous_Binned + Covariate_Categorical + Covariate_Binary, 
                               data = data, 
                               family = "binomial")
```

```{r}
# Data with propensity score and IPW weights as additional columns
data_propensity <- data %>%
  mutate(Propensity_ForBooster = predict(propensity_boosting_mod, type = "response")) %>% # Propensity for receiving booster column
  mutate(IPW_ForBooster = ifelse(Booster == 1, yes = 1 / Propensity_ForBooster, no = 1 / (1 - Propensity_ForBooster))) # IPW for receiving booster column
```

## Propensity Score Matching (with Caliper)

```{r}
# Generate nearest neighbor propensity score matches
# Using binned version of the continuous covariate is optional
data_prop_match <- matchit(Booster ~ Covariate_Continuous + Covariate_Categorical + Covariate_Binary, 
                             data = data, 
                             method = "nearest", # Specify nearest neighbor matching, can also use optimal matching but takes much longer
                             distance = "glm",
                             caliper = 0.2, # Specify caliper of 0.2
                             std.caliper = TRUE) %>% # Specify that caliper is based on standard deviation of propensity scores
  match.data() %>% # This function call is necessary for a dataframe to be output\
  mutate(ipw = ifelse(Booster == 1, yes = 1 / distance, no = 1 / (1 - distance))) # Can also generate IPW
# Matching strata of observations are denoted by new 'subclass' column in dataframe
```

### Propensity Score Matched Models

#### Unconditional Logistic Regression

```{r}
mod_prop_match_lr <- glm(Test_Result ~ Booster, family = "binomial", data = data_prop_match)
summary(mod_prop_match_lr)
paste("VE =", 1 - exp(coef(mod_prop_match_lr)["Booster1"]))
```

#### Conditional Logistic Regression

```{r}
# 'clogit()' requires a numeric or logical outcome variable
# Given that we stored 'Test_Result' as a factor, we coerce it to a numeric variable
mod_prop_match_clr <- clogit(as.numeric(Test_Result) ~ Booster + strata(subclass), data = data_prop_match)
summary(mod_prop_match_clr)
paste("VE =", 1 - exp(coef(mod_prop_match_clr)["Booster1"]))
```

### Propensity Score Adjustment Models

#### No Direct Model Adjustment

```{r}
# Same model as unadjusted model, but include propensity score as a term
mod_prop_adj_lr <- glm(Test_Result ~ Booster + Propensity_ForBooster, family = "binomial", data = data_propensity)
summary(mod_prop_adj_lr)
paste("VE =", 1 - exp(coef(mod_prop_adj_lr)["Booster1"]))
```

#### Direct Model Adjustment

```{r}
# Include terms used to generate propensity score as covariates in VE model as well
# Same model as adjusted model, but include propensity score as a term
mod_prop_adj_direct_lr <- glm(Test_Result ~ Booster + Propensity_ForBooster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, family = "binomial", data = data_propensity)
summary(mod_prop_adj_direct_lr)
paste("VE =", 1 - exp(coef(mod_prop_adj_direct_lr)["Booster1"]))
```

### Inverse Probability Weighting Models

#### No Direct Model Adjustment

```{r}
# Same model as unadjusted model, but include weights argument
mod_prop_ipw_lr <- glm(Test_Result ~ Booster, family = "binomial", weights = IPW_ForBooster, data = data_propensity)
summary(mod_prop_ipw_lr)
paste("VE =", 1 - exp(coef(mod_prop_ipw_lr)["Booster1"]))
```

#### Direct Model Adjustment

```{r}
# Same model as adjusted model, but include weights argument
mod_prop_ipw_direct_lr <- glm(Test_Result ~ Booster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, family = "binomial", weights = IPW_ForBooster, data = data_propensity)
summary(mod_prop_ipw_direct_lr)
paste("VE =", 1 - exp(coef(mod_prop_ipw_direct_lr)["Booster1"]))
```



