---
title: "Cohort Code Demo"
author: "Sabir Meah"
date: "2023-06-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(survival)
library(survminer)
library(MatchIt)
```

# Data Generation

We generate a sample of 1,000 tests to use for the generation. Variables include an indicator for booster status, an indicator for infection during period, and three covariates: one continuous, one categorical, and one binary.

```{r}
set.seed(612421) # Set a seed for reproducibility

data <- cbind.data.frame(
  Booster = as.factor(sample(c(0, 1), size = 1000, prob = c(0.5, 0.5), replace = TRUE)), # Indicator for if individual received booster or not (0 no, 1 yes)
  Infection = sample(c(0, 1), size = 1000, prob = c(0.8, 0.2), replace = TRUE), # Indicator for infection during study period (0 no, 1 yes)
  Covariate_Continuous = runif(n = 1000, min = 0, max = 50), # Continuous covariate ranging between 0 and 50
  Covariate_Categorical = as.factor(sample(c("A", "B", "C", "D", "E"), size = 1000, prob = rep(0.2, 5), replace = TRUE)), # Categorical covariate with 5 levels
  Covariate_Binary = as.factor(sample(c(0, 1), size = 1000, prob = c(0.5, 0.5), replace = TRUE)) # Binary covariate
)
```

We also create a survival time (days under observation before an infection or censoring event) variable in days.  We use a data generating mechamism that gives a 20% probability of infection, and a uniformly random day of infection within the 30 day study period.  For uninfected individuals, we have an 80% probability of censoring at the end of the 30 day study period, and a 20% probability of censoring before the end of the study at a uniformly random day within the 30 day study period.

```{r}
set.seed(612421) # Set a seed for reproducibility

study_length <- 30 # Set 30 day total study period

Survival_Time <- rep(NA_real_, nrow(data))
for(i in 1:nrow(data)){
  rand_day = sample(1:study_length, size = 1) # Draw a random day
  if(data[i,]$Infection == 1){ # If subject was infected
    Survival_Time[i] <- rand_day # Use random day as the day of the event
  } else {
    if(runif(n = 1, min = 0, max = 1) > 0.8){ # If subject was uninfected, give 80% chance of end of study censoring
      Survival_Time[i] <- rand_day # And 20% change of censoring during study, where we sett it as the random day
    } else {
      Survival_Time[i] <- study_length
    }
  }
}

data <- data %>%
  mutate(Survival_Time = Survival_Time)
```

# Models Without Matching or Propensity Scores

## Models

### Kaplan-Meier Curve

```{r}
ggsurvplot(survfit(Surv(time = Survival_Time, event = Infection) ~ Booster, data = data),
           data = data,
           conf.int = TRUE,
           fun = "cumhaz")
```


### Unadjusted Model

```{r}
mod_unadj <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster, data = data)
summary(mod_unadj)
paste("VE =", 1 - exp(coef(mod_unadj)["Booster1"]))
```

### Adjusted Model

```{r}
mod_adj <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, data = data)
summary(mod_adj)
paste("VE =", 1 - exp(coef(mod_adj)["Booster1"]))
```

# Exact Matching

## Match Generation

This dataframe will be used for the propensity score adjustment and IPW models.

```{r}
# Binning continuous covariate
# Can be done along any division of your choosing, specify cutpoints with 'breaks' argument
data <- data %>%
  mutate(Covariate_Continuous_Binned = cut(Covariate_Continuous, breaks = seq(0, 50, by = 10)))
```

This dataframe will be used for just the propensity score caliper matching model.

```{r}
# Generate exact matches
# Make sure to use the binned version of the continuous covariate
data_exact_match <- matchit(Booster ~ Covariate_Continuous_Binned + Covariate_Categorical + Covariate_Binary, 
                             data = data, 
                             method = "exact") %>%
  match.data() # This function call is necessary for a dataframe to be output
# Matching strata of observations are denoted by new 'subclass' column in dataframe
```

## Matched Models

### Unstratified Cox Regression

```{r}
mod_exact <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster, data = data_exact_match)
summary(mod_exact)
paste("VE =", 1 - exp(coef(mod_exact)["Booster1"]))
```

### Stratified Cox Regression

```{r}
mod_exact_strat <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + strata(subclass), data = data_exact_match)
summary(mod_exact_strat)
paste("VE =", 1 - exp(coef(mod_exact_strat)["Booster1"]))
```

# Propensity Score Models

## Propensity Score Generation

```{r}
# Logistic model generating propensity score by predicting exposure (vaccination)
# Can similarly be done to generate a propensity for testing score by replacing 'Booster' with testing variable
propensity_boosting_mod <- glm(Booster ~ Covariate_Continuous_Binned + Covariate_Categorical + Covariate_Binary, 
                               data = data, 
                               family = "binomial")
```

```{r}
# Data with propensity score and IPW weights as additional columns
data_propensity <- data %>%
  mutate(Propensity_ForBooster = predict(propensity_boosting_mod, type = "response")) %>% # Propensity for receiving booster column
  mutate(IPW_ForBooster = ifelse(Booster == 1, yes = 1 / Propensity_ForBooster, no = 1 / (1 - Propensity_ForBooster))) # IPW for receiving booster column
```

## Propensity Score Matching (with Caliper)

```{r}
# Generate nearest neighbor propensity score matches
# Using binned version of the continuous covariate is optional
data_prop_match <- matchit(Booster ~ Covariate_Continuous + Covariate_Categorical + Covariate_Binary, 
                             data = data, 
                             method = "nearest", # Specify nearest neighbor matching, can also use optimal matching but takes much longer
                             distance = "glm",
                             caliper = 0.2, # Specify caliper of 0.2
                             std.caliper = TRUE) %>% # Specify that caliper is based on standard deviation of propensity scores
  match.data() %>% # This function call is necessary for a dataframe to be output
  mutate(ipw = ifelse(Booster == 1, yes = 1 / distance, no = 1 / (1 - distance))) # Can also generate IPW
# Matching strata of observations are denoted by new 'subclass' column in dataframe
```

### Propensity Score Matched Models

#### Unstratified Cox Regression

```{r}
mod_prop_match <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster, data = data_prop_match)
summary(mod_prop_match)
paste("VE =", 1 - exp(coef(mod_prop_match)["Booster1"]))
```

#### Stratified Cox Regression

```{r}
mod_prop_match_strat <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + strata(subclass), data = data_prop_match)
summary(mod_prop_match_strat)
paste("VE =", 1 - exp(coef(mod_prop_match_strat)["Booster1"]))
```

### Propensity Score Adjustment Models

#### No Direct Model Adjustment

```{r}
# Same model as unadjusted model, but include propensity score as a term
mod_prop_adj <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + Propensity_ForBooster, data = data_propensity)
summary(mod_prop_adj)
paste("VE =", 1 - exp(coef(mod_prop_adj)["Booster1"]))
```

#### Direct Model Adjustment

```{r}
# Include terms used to generate propensity score as covariates in VE model as well
# Same model as adjusted model, but include propensity score as a term
mod_prop_adj_direct <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + Propensity_ForBooster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, data = data_propensity)
summary(mod_prop_adj_direct)
paste("VE =", 1 - exp(coef(mod_prop_adj_direct)["Booster1"]))
```

### Inverse Probability Weighting Models

#### No Direct Model Adjustment

```{r}
# Same model as unadjusted model, but include weights argument
mod_prop_ipw <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster, weights = IPW_ForBooster, data = data_propensity)
summary(mod_prop_ipw)
paste("VE =", 1 - exp(coef(mod_prop_ipw)["Booster1"]))
```

#### Direct Model Adjustment

```{r}
# Same model as adjusted model, but include weights argument
mod_prop_ipw_direct <- coxph(Surv(time = Survival_Time, event = Infection) ~ Booster + Covariate_Continuous + Covariate_Categorical + Covariate_Binary, weights = IPW_ForBooster, data = data_propensity)
summary(mod_prop_ipw_direct)
paste("VE =", 1 - exp(coef(mod_prop_ipw_direct)["Booster1"]))
```






